\documentclass[12pt]{article}

% Use Times (Times New Roman-like) font
\usepackage{times}

% Set page margins
\usepackage[margin=1in]{geometry}

% For 1.5 line spacing
\usepackage{setspace}

% For custom headers/footers
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
\fancyfoot[C]{{i}} % Centered page number

% Remove the top horizontal line
\renewcommand{\headrulewidth}{0pt}
\begin{document}
	
	\begin{center}
		{\Large \bf Abstract}
	\end{center}

    \vspace{20pt}
	
	\onehalfspacing % Set 1.5 line spacing for the text that follows
	
	\textit{In today’s era of AI-driven education, communication skills and interview readiness have become critical requirements for career development. This system is designed with the goal of providing an AI-based multilingual virtual interviewing platform, where candidates can practice, learn, and evaluate their performance across multiple languages under a single interface — making the process more accessible, interactive, and efficient. The proposed system bridges the gap between theoretical interview preparation, real-time practice, and AI-powered assessments with instant feedback. It offers a unified environment where users can engage in mock interviews, receive performance analytics, and improve language proficiency without switching between platforms — thereby enhancing focus, efficiency, and overall learning outcomes. The methodology integrates a sequence of intelligent modules that collectively form a comprehensive interview training ecosystem. The system includes multiple components dedicated to AI interviewing, proctoring, speech evaluation, emotion analysis, and gamified performance tracking. This approach provides several advantages such as real-time feedback, adaptive questioning, multilingual interaction, and secure evaluation mechanisms — all of which prepare learners for real-world interview challenges with discipline and confidence. Overall, the system promotes self-paced learning, continuous skill enhancement, and global language adaptability, helping candidates build the communication and interview skills required in today’s fast-evolving job market.}
	
	\vspace{1em} % Add vertical space between abstract and keywords
	
	\noindent
	\textbf{Keywords:}\textit{ AI Interview Simulation, Multilingual Interaction, Virtual Interview Training, Skill Development.}
	
\end{document}
