\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}  % 1-inch margins
\usepackage{times}                 % Times New Roman–like font
\usepackage{setspace}              % For line spacing
\usepackage{fancyhdr}              % For custom headers/footers
\usepackage{ragged2e}              % For \justifying

\setstretch{1.5}                   % 1.5 line spacing

\pagestyle{fancy}
\fancyhf{} % Clear default header and footer

% Head er on the right side
\fancyhead[R]{Saksham AI: Multilingual Virtual Interviewer}

% Footer on the left side
\fancyfoot[L]{Pillai HOC College of Engineering \& Technology (Autonomous), Rasayani}
\fancyfoot[R]{\thepage}

% Horizontal lines in header & footer
\renewcommand{\headrulewidth}{0.4pt} 
\renewcommand{\footrulewidth}{0.4pt}

% Set the page number to start from 48
\setcounter{page}{51}

\begin{document}

\justifying
\noindent
\begin{center}
{\Large \textbf{Acknowledgement}}\\[0.6cm]
\end{center}
\justifying

 It is a privilege for us to have been associated with \textbf{Dr. Suchita Walke} , our guide, during
 this project work. We have been greatly benefited by her valuable suggestions and ideas. It
 is with great pleasure that we express our deep sense of gratitude to them for their valuable
 guidance, constant encouragement and patience throughout this work. We are also indebted to
 our guide for extending the help to academic literature. We express our gratitude to \textbf{Prof. Nikita
 Saindane} (Project Coordinator), \textbf{Dr. Rajashree Gadhave} (Head of Department of Computer
 Engineering), \textbf{Dr. Jagdish W. Bakal} (Principal) for their constant encouragement, cooperation
 and support. We take this opportunity to thank all our classmates for their company during the
 course work and for useful discussion we had with them. We would be failing in our duties if
 we do not make a mention of our family members, including our parents for providing moral
 support, without which this work would not have been completed.
\\
\\
Thanking you,
\vspace{1cm}

\begin{flushright}
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{{Rupali Gandotra}} \\[1cm]
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{{Aaditya Jadhav}}\\[1cm]
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{{Sanskruti Kadam}}\\
\end{flushright}


\end{document}
