\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}

\fancyhead[R]{Saksham AI: Multilingual Virtual Interviewer}

\fancyfoot[L]{Pillai HOC College of Engineering \& Technology (Autonomous), Rasayani}
\fancyfoot[R]{\thepage}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\setcounter{page}{49}

{\LARGE \textbf{References}}

\vspace{15pt}

\begin{enumerate}[label={[{\arabic*}]}, leftmargin=1cm]

\item Santhush Chandrasekara, Dileep Hewavitharana, Maleesha Weerasinghe, Binod Gayasri, ``AI-Powered Virtual Interviewer for Multilingual Job Applicants", published in International Research Conference on Smart Computing and Systems Engineering (SCSE), 2025.

\item Max Hort, Leon Moonen, ``InterviewEval: Dataset of Multilingual Responses for AI-Based Candidate Evaluation", published in IEEE Conference on Software Testing, Verification and Validation (ICST), 2025.

\item E. Elancheziyan, A. Vishnu, K. C. Sanjay, V. Thayanithimaran, “AI Powered Virtual Job Interview Simulation System”, published in IRE Journals, 2025.

\item Tanishque Sharma, Anmol Singh, “AI-Powered Mock Interview Platform Using Computer Vision and NLP”, published in International Journal of Innovative Research in Engineering & Multidisciplinary Physical Sciences (IJIRMPS), 2025.

\item Yuki Tanaka, Linda Foster, “A Multimodal Framework for Evaluating Candidate Confidence and Technical Proficiency in AI-Driven Assessments”, published in IEEE/WIC/ACM International Conference on Web Intelligence, 2025.

\item Rahul Desai, Sneha Patil, “AI-Powered Interview System Based On Resume Analysis”, published in International Journal of Scientific Research and Engineering Trends (IJSRET), 2025.

\item Md. Musab Haqqani, Ganesh B. Regulwar, Boinipally Ayush Goud, Sai Poojitha Veggalam, ``Bridging Communication Gaps with AI-Driven Virtual Interview Platforms", published in IEEE North Karnataka Subsection Flagship International Conference (NKCon), 2024.

\item Santhosh Krishna B V, Ms. Neha Jadhav, Kamisetty Jahnavi, ``Identity-Aware Feedback Systems in AI Interviewers", published in Ninth International Conference on Communication and Electronics Systems (ICCES), 2025.

\item Akram Nishanov, Oybek Allamov, Janar Yusupova, ``Developing AI Methodologies for Multilingual Interview Simulations", published in IEEE 3rd International Conference on Problems of Informatics, Electronics and Radio Engineering (PIERE), 2024.

\item Prof. Sampada Kulkarni, Avneesh Deshmukh, Mihika Saraf, Kedar Chikane, Soham Rane, “Enhancing Candidate Focus During Virtual Interviews Using AI-driven Interactive Interfaces” published in International Journal of Creative Research Thoughts (IJCRT), 2024

\item Mohammed Ali, John Smith, Emily Carter, “Scalable Architecture for High-Volume Automated Resume Processing and Interview Scheduling”, published in International Conference on Cloud Computing and Services Science, 2024.

\item Jiannong Cao, Zhiyuan Wen, “InterviewAI: A Multiagent System for Personalized and Adaptive Interview Experience” published in 2025

\item Anita Sukarno, “Transforming Recruitment from Interviewer-centered to Candidate-centered Learning via AI” published in Indonesian Journal of Computer and Cognitive Science, 2025

\item Dr. Madhur Jain, Dr. Shilpi Jain, Nipun Baryah, “InterViewBot: An Intelligent Multilingual Platform with Real-time AI Feedback” published in International Journal of Scientific Research in Computer Science, Engineering and Information Technology, 2025

\end{enumerate}

\end{document}