\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\setstretch{1.5}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{AyurSpace}
\fancyfoot[L]{Pillai HOC College of Engineering \& Technology (Autonomous), B. E. Computer Engineering}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\justifying
\noindent
\begin{center}
  {\Large \textbf{Acknowledgement}}\\[0.6cm]
\end{center}
\justifying

It is a privilege for us to have been associated with \textbf{Prof. Abhijeet More}, our guide, during
this project work. We have been greatly benefited by his valuable suggestions and ideas. It is
with great pleasure that we express our deep sense of gratitude to him for his valuable guidance,
constant encouragement, and patience throughout this work. We are also indebted to our guide for
extending the help to academic literature.

We express our gratitude to \textbf{Ms. Nikita Saindane} (Project Coordinator),
\textbf{Dr. Rajashree Gadhave} (Head of Department of Computer Engineering),
and \textbf{Dr. Jagdish W. Bakal} (Principal) for their constant encouragement, cooperation, and
support throughout the project.

We would also like to thank the teams at \textbf{Google Gemini} and \textbf{Plant.id (Kindwise)} for
providing the AI APIs that form the intelligence backbone of AyurSpace. We take this opportunity
to thank all our classmates for their company during the course work and for the useful discussions
we had with them. We would be failing in our duties if we do not make mention of our family
members, including our parents, for providing moral support, without which this work would not
have been completed.

\\
\\
Thanking you,
\vspace{1cm}

\begin{flushright}
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{Pratik Nitin Pisal} \\[1cm]
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{Soham Govardhan Patil} \\[1cm]
    \rule{6cm}{0.5pt} \\[-0.4cm]\\[0.1cm]
    \makebox[6cm]{Pranav Shashikant Kamble} \\
\end{flushright}

\end{document}
