\documentclass[12pt]{article}

\usepackage[paperwidth=612pt,paperheight=792pt,top=72pt,bottom=72pt,left=30mm,right=20mm]{geometry}
\usepackage{times}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{enumitem}
\setstretch{1.5}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{AyurSpace}
\fancyfoot[L]{Pillai HOC College of Engineering \& Technology (Autonomous), B. E. Computer Engineering}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\begin{document}

\begin{center}
  {\Large \textbf{References}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=*, label={[\arabic*]}]

    \item Waldchen, J., Rzanny, M., Seeland, M., and Mader, P. (2018). ``Automated plant species
    identification---Trends and future directions.'' \textit{PLOS Computational Biology}, 14(4).

    \item Singhal, K., Azizi, S., Tu, T., et al. (2023). ``Large language models encode clinical
    knowledge.'' \textit{Nature}, 620, 172--180.

    \item Martin, R. C. (2017). \textit{Clean Architecture: A Craftsman's Guide to Software
    Structure and Design}. Prentice Hall.

    \item Google LLC. (2024). ``Gemini API Documentation.'' \textit{Google AI for Developers}.
    Retrieved from https://ai.google.dev/

    \item Kindwise. (2024). ``Plant.id API v3 Documentation.'' \textit{Kindwise Developer Portal}.
    Retrieved from https://plant.id/

    \item World Health Organization. (2023). ``WHO Traditional Medicine Strategy 2025--2034.''
    \textit{WHO Publications}.

    \item Frawley, D. (2000). \textit{Ayurvedic Healing: A Comprehensive Guide} (2nd ed.).
    Lotus Press.

    \item Firebase Team. (2024). ``Firebase Authentication and Firestore Documentation.''
    \textit{Google Firebase}. Retrieved from https://firebase.google.com/docs

    \item Flutter Team. (2024). ``Flutter Documentation.'' \textit{Flutter.dev}.
    Retrieved from https://flutter.dev/docs

    \item Laddha, A., and Mahajan, U. (2021). ``Computational Approaches in Ayurvedic Medicine:
    A Systematic Review.'' \textit{Journal of Ethnopharmacology}, 267, 113491.

    \item Nair, R., and Kalariya, T. (2022). ``Mobile Applications for Herbal Plant
    Identification: A Review.'' \textit{International Journal of Computer Applications}, 185(1).

    \item Riverpod. (2024). ``Riverpod State Management Documentation.''
    Retrieved from https://riverpod.dev/docs

    \item GoRouter. (2024). ``GoRouter Navigation Package Documentation.''
    Retrieved from https://pub.dev/packages/go\_router

    \item Howard, A., et al. (2019). ``Searching for MobileNetV3.'' In \textit{Proceedings of the
    IEEE/CVF International Conference on Computer Vision (ICCV)}, 1314--1324.

\end{enumerate}

\end{document}
