\section{Conclusion}
The creation of \textbf{AyurSpace} is a key step in the digital preservation and
democratization of Ayurvedic knowledge. By executing a hybrid neuro-symbolic architecture,
this framework addresses the major problems facing current plant identification
tools---absence of medicinal context and risk of generative hallucinations. Experimental
findings (96.4\% taxonomy accuracy, 99.1\% contextual reasoning compliance) confirm the
effectiveness of decoupling visual recognition from semantic analysis. The algorithmic
formalization of the \textit{Dosha} assessment transforms subjective clinical intuition
into replicable digital logic, enabling smart health decisions based on ancient wisdom
merged with robust modern mobile processing.

\section{Limitations}
The current implementation of AyurSpace has several limitations. Both AI APIs---Plant.id and Google Gemini---require an active internet connection, which restricts usability in areas with poor connectivity. The usage-based pricing models of these APIs limit high-volume production deployment. Additionally, the Plant.id dataset may under-represent rare Indian medicinal herbs, potentially affecting identification accuracy for region-specific species. While the hybrid neuro-symbolic pipeline significantly mitigates LLM hallucinations, it does not fully eliminate them, necessitating continued caution in critical health-related recommendations.

\section{Future Scope}
Several promising directions exist for the future development of AyurSpace. Edge AI optimization through quantized MobileNet models (int8) would enable complete offline plant identification on device, resolving connectivity issues in rural areas. Augmented Reality (AR) interfaces using ARCore could overlay medicinal properties, alerts, and plant structures directly on the camera viewfinder, enhancing the user experience. A ``Vaidya Connect'' telemedicine integration component could link user Dosha baselines and scan histories with licensed Ayurvedic practitioners' dashboards, bridging the gap between digital tools and traditional clinical practice.
