\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}  % 1-inch margins
\usepackage{times}                 % Times New Roman–like font
\usepackage{setspace}              % For line spacing
\usepackage{fancyhdr}              % For custom headers/footers
\usepackage{ragged2e}              % For \justifying

\setstretch{2.0}                   % 1.5 line spacing

\pagestyle{fancy}
\fancyhf{} % Clear default header and footer

% Header (Right-aligned)
\fancyhead[R]{\small Ultrasound Nerve Imaging And CLinical Decision Support System}

% Footer (Left-aligned: College Name, Right-aligned: Page Number)
\fancyfoot[L]{\small Pillai HOC College of Engineering and Technology, Rasayani}
\fancyfoot[R]{\small \thepage}

% Horizontal lines in header & footer
\renewcommand{\headrulewidth}{0.4pt} 
\renewcommand{\footrulewidth}{0.4pt} 


% Set the page number to start from 63
\setcounter{page}{65}

\begin{document}

\justifying
\noindent
\begin{center}
{\Large \textbf{Acknowledgement}}\\[0.6cm]
\end{center}
\justifying

\noindent It is a privilege for us to have been associated with \textbf{Prof. Abhijeet More}, our guide, during
this project work. We have been greatly benefited by her valuable suggestions and ideas. It
is with great pleasure that we express our deep sense of gratitude to them for their valuable
guidance, constant encouragement and patience throughout this work. We are also indebted
to our guide for extending the help to academic literature. We express our gratitude to \textbf{Prof.
Nikita Saindane} (Project Coordinator), \textbf{Dr. Rajashree Gadhave} (Head of Department of
Computer Engineering),\textbf{Dr. Jagdish W. Bakal} (Principal) for their constant encouragement,
cooperation and support. We take this opportunity to thank all our classmates for their company
during the course work and for useful discussion we had with them. We would be failing in our
duties if we do not make a mention of our family members, including our parents for providing
moral support, without which this work would not have been completed.
Thanking You,
\vspace{1cm}

\begin{flushright}
  
    \makebox[6.4cm]{\textbf{Sumit Patil}} \\[0.3cm]
   
    \makebox[6cm]{\textbf{Pratik Vehele}}
\end{flushright}


\end{document}