\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
    \item World Health Organization, \textit{WHO Traditional Medicine Strategy: 2014--2023}.
    World Health Organization, Geneva, 2013.

    \item Kindwise Inc., ``Plant.id API Documentation,'' 2024. [Online]. Available:
    https://web.plant.id/api-v2. [Accessed: Jan. 29, 2026].

    \item Google DeepMind, ``Gemini: A Family of Highly Capable Multimodal Models,''
    \textit{arXiv preprint arXiv:2312.11805}, 2023.

    \item S. Singhal et al., ``Large Language Models Encode Clinical Knowledge,''
    \textit{Nature}, vol. 620, pp. 172--180, 2023.

    \item J. W\"{a}ldchen and P. M\"{a}der, ``Identifying Plant Species Using Computer
    Vision Techniques: A Systematic Literature Review,'' \textit{Archives of Computational
    Methods in Engineering}, vol. 25, no. 2, pp. 507--543, 2018.

    \item R. Martin, \textit{Clean Architecture: A Craftsman's Guide to Software Structure
    and Design}. Prentice Hall, 2017.

    \item Google, ``Flutter Architectural Overview,'' 2024. [Online]. Available:
    https://flutter.dev/go/arch. [Accessed: Jan. 29, 2026].

    \item R. Remigius, ``Riverpod: A Reactive State-Management Framework for Flutter,''
    2023. [Online]. Available: https://riverpod.dev.

    \item P. V. Sharma, \textit{Dravya Guna Vijnana}, vol. 1. Varanasi, India:
    Chaukhambha Bharati Academy, 2006.

    \item V. Lad, \textit{Textbook of Ayurveda: Fundamental Principles}, vol. 1.
    Ayurvedic Press, 2002.

    \item S. Kumar, A. Gupta, and R. Singh, ``Automated Identification of Medicinal
    Plants Using Deep Convolutional Neural Networks,'' \textit{Journal of King Saud
    University -- Computer and Information Sciences}, vol. 35, no. 4, pp. 1--12, 2023.

    \item A. Affouard, P. Bonnet, M. Lombardo, J.-C. Melet, C. Perronne, A. Quintero,
    H. Chouiref, C. Blanc, A. Champ{\'e}, A. El Mahrach, and A. Joly, ``Pl@ntNet App
    in the Era of Deep Learning,'' \textit{iScience}, vol. 24, no. 7, p. 102910, 2021.

    \item L. Laranjo, A. Dunn, H. Tong, B. Kocaballi, J. Chen, R. Bashir,
    D. Surian, B. Gallego, F. Magrabi, A. Y. S. Lau, and E. Coiera,
    ``Conversational Agents in Healthcare: A Systematic Review,''
    \textit{Journal of the American Medical Informatics Association},
    vol. 25, no. 9, pp. 1248--1258, 2018.

    \item R. Patel and A. Sharma, ``A Digital Framework for Tridosha-Based Health
    Assessment Using Machine Learning,'' \textit{International Journal of Ayurveda
    Research}, vol. 12, no. 3, pp. 45--54, 2021.

    \item P. Mehta, S. Joshi, and K. Rao, ``AI-Powered Personalized Wellness
    Applications: A Systematic Review,'' \textit{Journal of Medical Internet Research},
    vol. 24, no. 6, e35199, 2022.

    \item A. Raj, S. Verma, and M. Patel, ``Flutter for Cross-Platform Mobile Health
    Applications: Performance and Usability Analysis,'' \textit{International Journal
    of Mobile Computing and Multimedia Communications}, vol. 14, no. 2, pp. 1--18, 2023.
\end{enumerate}
