\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\textit{The amalgamation of traditional medicinal knowledge with contemporary mobile
computing and artificial intelligence (AI) offers a revolutionary prospect for global
healthcare accessibility. Ayurveda, the ancient Indian medical system, fundamentally
depends on the accurate identification of medicinal plants and the individualized
evaluation of body constitution (Dosha). But most people still cannot get this
information because there are not enough experts and taxonomic identification is hard.
This report introduces \textbf{AyurSpace}, a cross-platform mobile framework created
with Flutter that utilizes an innovative hybrid AI architecture. The system combines
Plant.id, a specialized taxonomic classifier for high-accuracy botanical identification,
with Google Gemini, a large language model for contextual Ayurvedic reasoning. It also
digitizes the tridosha assessment process by using a weighted algorithmic scoring model.
We delineate the system architecture, the integration of RESTful AI microservices, and
the formalization of Ayurvedic data models. Experimental evaluation shows that the
hybrid approach works well to connect botanical accuracy with medical context, achieving
a 96.4\% accuracy in taxonomy and a 99.1\% compliance in contextual reasoning, offering
a scalable solution for preserving digital heritage and improving personal health.}

\vspace{0.5cm}
\noindent\textbf{Keywords}\textit{---Ayurveda, Mobile Computing, Generative AI, Plant
Identification, Computer Vision, Gemini API, Flutter, Digital Health}
